---
title       : Jijou's app
subtitle    : Find interesting places around you!
author      : Joanne Breitfelder
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]           
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- 
## Presentation of the application 

Jijou's app allows you to find interesting places around you. Looking for a good pizzeria, an aquarium, or the closest dentist? This app is for you! :) 

```{r, out.width=1000, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
include_graphics("appli.pdf")
```  

- *En tant qu'utilisateurs on est conquis!*
**Mélanie, France**
- *On aime beaucoup le design, le retour à la simplicité!*
**Damien, France**
- *Súper chévere y facil de usar! Aunque no encontré la pizzeria al lado de mi casa..* 
**Juan, Brazil**  

--- 
## General information 

- **The application:** <https://jijou.shinyapps.io/Jijou-s-app/>
- **My Github repository:** <https://github.com/jbreitfelder/Jijou-s-app>
- This application is based on [RStudio's Shiny](http://shiny.rstudio.com) and [Google Maps API](https://developers.google.com/maps/).

```{r, out.width=600, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
include_graphics("logos.pdf")
```  

### How to use the app?

- Enter the kind of place you are looking for.
- Enter your location
- Choose the radius in which you want to look for 
- Adjust the map zoom: from 3 (continent) to 21 (building).
- Actualize and enjoy! :)  

---
## Geocoding with Google Maps

The application is based on 2 functions using Google Maps API. The first one, `geoCode()`, allows to find the GPS coordinates of a given place. I found this function [here](https://gist.github.com/josecarlosgonz/6417633).

### Utilisation example:

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(shiny)
library(RCurl)
library(jsonlite)
library(plyr)
library(ggmap)
library(curl)

url <- function(address, return.call="json", sensor="false") {
        root <- "http://maps.google.com/maps/api/geocode/"
        u <- paste(root, return.call, "?address=", 
                   address, "&sensor=", sensor, sep="")
        return(URLencode(u))
}

geoCode <- function(address) {
        u <- url(address)
        doc <- getURL(u)
        x <- fromJSON(doc, simplifyVector=FALSE)
        if(x$status=="OK") {
                lat <- x$results[[1]]$geometry$location$lat
                lng <- x$results[[1]]$geometry$location$lng
                location_type <- x$results[[1]]$geometry$location_type
                formatted_address <- x$results[[1]]$formatted_address
                return(c(lat, lng, location_type, formatted_address))
        } else {
                return(c(NA, NA, NA, NA))
        }
}
```

```{r}
geoCode("Paris, France")
```

### Explanation of the result:

The first two items are the **latitude** and **longitude** coordinates, the third item is the **location type** ("ROOFTOP", "RANGE_INTERPOLATED", "GEOMETRIC_CENTER" or "APPROXIMATE") and the last one is the **formatted address**.

---
## Finding places of interest with Google Maps API

The second function, `close_places()` returns the 20 closest places of interest around a given position. 

### Utilisation example :

```{r, echo=FALSE, message=FALSE, warning=FALSE}
close_places <- function(location, radius, place){ 
        
        ## Coordinates of the location
        coord <- geoCode(location)
        coord <- paste(as.character(round(as.numeric(coord[1]), 5)), 
                       as.character(round(as.numeric(coord[2]), 5)), sep=",")
        
        ## Creation of the URL
        baseurl<-"https://maps.googleapis.com/maps/api/place/nearbysearch/json?"
        google_key <- "AIzaSyD-8mknrSyCYh0Feg5PgGmq8gFIh3GINJo"
        newurl <- paste(baseurl,"location=", coord,
                        "&radius=", radius,
                        "&name=", place,
                        "&key=", google_key, sep="")
        
        ## Results
        final <- fromJSON(newurl, simplifyVector=TRUE)
        final <- final$results
        
        if("opening_hours" %in% names(final)){
                if("open_now" %in% names(final$opening_hours)){
                        open_now <- ifelse(is.na(final$opening_hours$open_now), "No information",
                                         ifelse(final$opening_hours$open_now==FALSE,
                                                "Closed :(", "Open :)"))
                }
        } else {
                open_now <- rep("No information", length(final$name))
        }
        
        rating <- ifelse(is.na(final$rating), mean(final$rating, na.rm=TRUE),
                         final$rating)
        
        icon <- paste("<img src='", final$icon, "' width='50'></img>", sep="")
        
        details <- data.frame(icon=icon,
                              rating=rating,
                              address=final$vicinity,
                              open_now=open_now,
                              name=final$name,
                              idx=1:length(final$geometry$location$lat),
                              lat=final$geometry$location$lat,
                              long=final$geometry$location$lng)
        
        return(details)
}
```

```{r}
results <- close_places("Johns Hopkins University", 1000, "school")
kable(head(results, 3))
```